Adversarial State Aggregation

### 2019-12-28 minutia/paper/paper.tex
paper: state aggregation section added

    \section{Markov Decision Processes}
    Reinforcement learning problems can be formulated as an Markov decision process (MDP)\cite{Puterman1994}.
    Discrete discounted reward criterion is the center of focus for ease of exposition in this paper.
    For an environment and a decision maker, state space $S$ and action space $A$ are defined, respectively.
    The transition probabilities $T$ describe how likely is the next state $s'$ by taking a specific action $a$ by
    the agent in a certain state $s$ which will receive $r$ as reward.
    For a taken action $a_i$ in the state $s_i$, the decision maker will be ended up in state $s_{i+1}$ by the
    transition probabilities $P : S \times A \times S \rightarrow [0, 1]$ and wil receive reward $r_{i+1}$ from the
    rewards $R : S \times A \rightarrow \mathbb{R}$: \\
    \center $s_{i+1} = T(s_{i+1}|s_i, a_i)$ \\
    \center $r_{i+1} = R(s_i, a_i)$ \\

>>>>

    \section{Markov Decision Processes}
    Reinforcement learning problems can be formulated as an Markov decision process (MDP)\cite{Puterman1994}.
    Discrete discounted reward criterion is the center of focus for ease of exposition in this paper.
    For an environment and a decision maker, state space $S$ and action space $A$ are defined, respectively.
    The transition probabilities $T$ describe how likely is the next state $s'$ by taking a specific action $a$ by
    the agent in a certain state $s$ which will receive $r$ as reward.
    For a taken action $a_i$ in the state $s_i$, the decision maker will be ended up in state $s_{i+1}$ by the
    transition probabilities $P : S \times A \times S \rightarrow [0, 1]$ and wil receive reward $r_{i+1}$ from the
    rewards $R : S \times A \rightarrow \mathbb{R}$: \\
    \begin{equation}
        s_{i+1} = T(s_{i+1}|s_i, a_i)
    \end{equation}

    \begin{equation}
        r_{i+1} = R(s_i, a_i)
    \end{equation}

    \section{State Aggregation}
    State aggregation is an approximation approach to make a problem more tractable by a reduction in dimensionality in
    state space \footnote{aggregation in action space although is possible, has less significance comparatively.}.
    State aggregation, in particular, is a parametric feature-based approximation where the features are membership
    functions of 0-1 form.
    Aggregation groups similar states together, so called representative states, which lets the \textit{aggregate}
    problem to be
    solved by an exact
    method.
    The computed value function from the exact solution of the aggregate problem can be then used in the original
    problem.

    Now we formulate the aggregated problem by introducing the dynamics of the aggregate problem.
    The transition probabilities between two representative states:

    \begin{equation}
        \hat{p}_{x y}(u)=\sum_{j=1}^{n} p_{x j}(u) \phi_{j y},
    \end{equation}

    where $p_ {x j}$ is the transition probabilities from a representative state, $x$, to an original state, $j$
    and $\phi_{j y}$ is the aggregation probabilities from an original state, $j$, to a representative state, $y$.
    The rewards are defined as:

    \begin{equation}
        \hat{g}(x, u)=\sum_{j=1}^{n} p_{x j}(u) g(x, u, j)
    \end{equation}
